---
output:
  reprex::reprex_document:
    venue: "gh"
    advertise: FALSE
    session_info: TRUE
    style: TRUE
    comment: "#;-)"
    tidyverse_quiet: FALSE
    std_out_err: TRUE
knit: reprex::reprex_render
---

This template demonstrates many of the bells and whistles of the `reprex::reprex_document()` output format. The YAML sets many options to non-default values, such as using `#;-)` as the comment in front of output.

## Code style

Since `style` is `TRUE`, this difficult-to-read code (look at the `.Rmd` source file) will be restyled according to the Tidyverse style guide when it's rendered. Whitespace rationing is not in effect!

```{r}
x=1;y=2;z=x+y;z
```

## Quiet tidyverse

The tidyverse meta-package is quite chatty at startup, which can be very useful in exploratory, interactive work. It is often less useful in a reprex, so by default, we suppress this.

However, when `tidyverse_quiet` is `FALSE`, the rendered result will include a tidyverse startup message about package versions and function masking.

```{r, eval = requireNamespace("tidyverse", quietly = TRUE)}
library(tidyverse)
```

## Chunks in languages other than R

Remember: knitr supports many other languages than R, so you can reprex bits of code in Python, Ruby, Julia, C++, SQL, and more. Note that, in many cases, this still requires that you have the relevant external interpreter installed.

Let's try Python!

```{python, eval = Sys.which("python") != "", python.reticulate = requireNamespace("reticulate", quietly = TRUE)}
import pandas as pd
import numpy as np
from iSSVD.functions import issvd, issvd_diagnostics, gen_sim_vec, gen_tmp
from numpy.random import seed

seed(25)
data, rows, cols = gen_sim_vec(n=200,p=1000,D=2,rowsize=50, colsize=100, 
                               numbers=1,sigma=0.1,nbicluster=4, orthonm=False)

df = data[0]

res = issvd(X=df,standr=False,pointwise=True,steps=100,size=0.5,
            vthr = 0.9,ssthr=[0.6,0.65],nbicluster=10,rows_nc=False,cols_nc=False,col_overlap=False
            ,row_overlap=False,pceru=0.1,pcerv=0.1,merr=0.0001,iters=100)
```




